%-------------------------
% Resume in Latex
% Author : ChenxiaoNiu
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}  
  \textbf{\href{https://ncxinhanzhong.wixsite.com/niucx}{\Large Chenxiao Niu}} & Email : \href{niuc@mcmaster.ca}{niuc@mcmaster.ca}\\
  \href{https://ncxinhanzhong.wixsite.com/niucx}{https://ncxinhanzhong.wixsite.com/niucx} & Mobile : (+1)905-923-6358 \\
\end{tabular*}

%----------QUALIFICATIONS----------------
\section{Qualifications}
  \resumeSubHeadingListStart
     \resumeSubItem{Machine Learning}
      {Major in Machine Learning and skillful at modelling the algorithm as well as optimization.}
    \resumeSubItem{Software and Web Development}
      {Proficient in Software and Web Development, take part in practical projects.}
    \resumeSubItem{Code Management}
      {Good at Code Management and contribute to the University Greeting Website.}
    \resumeSubItem{Problem Solving}
      {Good at raising problems and solving problems in projects.}
  \resumeSubHeadingListEnd
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, Canada}
      {Master of Science in Electrical \& Computer Engineering;  Current GPA: 4.00}{Sep. 2017 -- Present}
    \resumeSubheading
      {Beijing University of Posts and Telecommunications}{Beijing, China}
      {Bachelor of Electronic Information Engineering;  Overall GPA: 3.xx (xx/xx)}{Sep. 2013 -- Jun. 2017}
  \resumeSubHeadingListEnd
  
  
 %-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    %% =========== BMW Internship ==========
    \resumeSubheading
      {BMW China}{Beijing, China}
      {IT Intern of Connected Drive}{Aug 2016 - Jan 2017}
      \resumeItemListStart
        \resumeItem{Greeting Robot}
          {Designed and Built a greeting robot used in the yearly BMW IT Roadshow, which has functionalities of NLP, Figure Detection as well as recommending car models to the guests.}
        \resumeItem{Scrum}
          {Imported Scrum workflow to the team, adjusted the conventional standard and formulated a customized regulation.}
         \resumeItem{Video Editing}
         {Edited a video for the team to compete the global IT Fair of BMW Group, and won the first place with a 50,000\$ award.} 
      \resumeItemListEnd
%
%    %% =========== Student Union ==========
%    \resumeSubheading
%      {Lucena Research}{Atlanta, GA}
%      {Data Scientist}{Summer 2012 and 2013}
%      \resumeItemListStart
%        \resumeItem{Portfolio Management}
%          {Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
%        \resumeItem{QuantDesk}
%          {Python backend for a web application used by hedge fund managers for portfolio management.}
%      \resumeItemListEnd
  \resumeSubHeadingListEnd
 
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
    %% ======= Website and Github management ========
      \resumeSubheading
      	{University Greeting Website}{Github, HTML}
	{Git, HTML, CSS, JS}{Sep 2017 - Present}
	\resumeItemListStart
	  \resumeItem{Github Management}
	  {Manage the website's branch every two days using git.}
	  \resumeItem{Website Update}
	  {Modify and Update the contents of the Website by using rst and html.}
	  \resumeItem{Issues Management}
	  {Publish issues of the website, assign and deal with the issues.}
	\resumeItemListEnd
	
   %% =========== Android Development ============
	\resumeSubheading
	  {Modern Art Application}{Android}
	  {Java}{Sep 2017 - Oct 2017}
	  \resumeItemListStart
	    \resumeItem{XML}
	    {Designed the layout of the application and created the User Interface in Android Studio by using XML.}
	    \resumeItem{Java}
	    {Imported and Implemented Android APIs using Java, realized functionalities such as Activity Invoking, SeekBar Listening and UI Interacting, etc.}
	   \resumeItemListEnd
    
   %% ======== Facial Expression Recognition System======   
   \resumeSubheading
      {Facial Expression Recognition System}{MATLAB}
      {Machine Learning}{Feb 2017 - Jun 2017}
      \resumeItemListStart
         \resumeItem{Gabor-Wavelet}
          {Detected and Captured the faces by using Gabor-Wavelet algorithm.}
      	\resumeItem{Data Preprocessing}
	 {Generalized and Normalized the JAFFE Database, extracted the features from the images using LBP, PCA and DCT algorithms.}    
        \resumeItem{Neural Network}
          {Constructed and trained the network in MATLAB, gained a 90\% accuracy of the test set.}
      \resumeItemListEnd	      

  
  %% ================= Web Spider ==============
  \resumeSubheading
  	{Web Spider}{Python}
	{Big Data, Data Analysis}{Mar 2016 - Apr 2016}
	\resumeItemListStart
		\resumeItem{Scrapy}
		{Set up and maintained a web spider by using Scrapy, which aims at ZhiHu (the biggest question-and-answer website in China) to find out the relationship between users and to study the social network.}
		\resumeItem{Social Network}
		{Acquired and analyzed thousand-level user data using Pajek, and figured out who are the most subscribed people and the links  between them.}
	\resumeItemListEnd
\resumeSubHeadingListEnd  


%--------SKILLS AND HONORS------------
\section{Skills \& Courses}
  \resumeSubHeadingListStart
    \item{
      \textbf{Skills}{: Java, Python, C++, Linux, Git, TensorFlow, MongoDB, MATLAB, HTML, CSS and JavaScript}
      
      \textbf{Courses}{: Machine Learning by Andrew Ng on Coursera; Programming Mobile Applications for Android Handheld Systems by U of Maryland on Coursera}
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
